---
title: "Forage Fitting"
author: "Tania Barychka"
date: "17/01/2020"
output: html_document
---

**Summary from data exploration**

1. Possible outliers in covariates and responses except for the Temperature.
2. Signs of collenarity between prey and predator body masses.
3. Attack rate increases near-linearly with predator and prey bodymass.
4. Handling times increases with prey body mass partiucalrly for invertebrates and vertebrates. Not as clear for protozoans.
No clear relationship with predator body mass.
Attack rates increase with both prey and predator body masses.
5. No significant interactions with temperature only. Some signs of interactions when broken into groups.


I will start with a model with no interactions. Apply the model, model selection, model validation. If the validation shows that there are patterns in the residuals, I will investigate why. Adding interactions may be an option to improve the model.


A. Attack rates
--

1.A Model with no interactions

```{r echo=FALSE}

```

B. Handling times
--
1.B Model with no interactions

```{r echo=FALSE}

```
