---
title: "Forage Fitting"
author: "Tania Barychka"
date: "17/01/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

**Summary from data exploration**

1. Possible outliers in covariates and responses except for the Temperature.
2. Signs of collenarity between prey and predator body masses.
3. Relationships:
- Handling times increases with prey body mass particucarly for invertebrates and vertebrates. Not as clear for protozoans.
Handling time increases more clearly with Prey/Predator bosy mass and slope looks more similar between groups.
No clear relationship with predator body mass.
- Attack rates increase with both prey and predator body masses.
- No clear relationships with temperature.
4.  No significant interactions with temperature only. Some signs of interactions when broken into groups.


I will start with a model with no interactions.


Attack rate ~ Predator Body mass + Prey Body mass+Temp


Handling time ~ Predator Body mass + Prey Body mass+Temp

Handling time ~ Prey/Predator body mass+Temp

Consider residuals.

Consider interaction with temperature.

Apply the model, model selection, model validation. If the validation shows that there are patterns in the residuals, I will investigate why. Adding interactions may be an option to improve the model.

```{r echo=FALSE, warning=FALSE, message=FALSE}

library (ggplot2)
library(dplyr)          # for data manipulation
library(tidyr)          # for data shaping
library(ggpubr)
library(gridExtra)
library(car)
library(lattice)
#work desktop
source("C:/Users/Tania Barychka/OneDrive/Desktop/HighstatLibV10.R")
library(RColorBrewer)

# Create customized color palette
library(colorBrewer)
mycol = c(brewer.pal(name="Dark2", n = 8), brewer.pal(name="Paired", n = 6))
```



```{r echo=FALSE}
#work
forage_db<- read.csv("C:/Users/Tania Barychka/OneDrive/Documents/Madingley Postdoc/resource_map_doi_10_5063_F17H1GTQ/data/FoRAGE_db_12_19_18_data_set.csv")
forage_db<-forage_db[-c(2084:2682),]

#summary(forage_db)


#home
#forage_db<- read.csv("C:/Users/Etherian/OneDrive/Documents/Madingley Postdoc/resource_map_doi_10_5063_F17H1GTQ/data/FoRAGE_db_12_19_18_data_set.csv")

#laptop
#forage_db<- read.csv("C:/Users/Tania/OneDrive/Documents/Madingley Postdoc/resource_map_doi_10_5063_F17H1GTQ/data/FoRAGE_db_12_19_18_data_set.csv")


#reduce data set to the variables we're interested in. I'll remove angiosperms and Nas.
forage_db$L.PredBM<-log10(forage_db$Predator.mass..mg.)
forage_db$L.PreyBM<-log10(forage_db$Prey.mass..mg.)
forage_db$L.Fitted.a..median.of.BS.samples.<-log10(forage_db$Fitted.a..median.of.BS.samples.)
forage_db$L.Fittted.h..day.<-log10(forage_db$Fittted.h..day.)

df<-cbind(forage_db$L.PredBM, forage_db$L.PreyBM, forage_db$L.Fitted.a..median.of.BS.samples., forage_db$L.Fittted.h..day., forage_db$Temp..C.., forage_db$Vert.invert)

colnames(df)<-c("LogPredBM", "LogPreyBM", "LogFittedAR", "LogFittedH_day", "Temp_c", "Vert.invert")

df<-as.data.frame(df)

df_no<-df[df$Vert.invert!="" & df$Vert.invert!="Angiosperm",]
head(df_no)

```


A. Attack rates
--

**Attack rate ~ Predator Body mass+Prey Body Mass+Temp_c**

```{r}

m1<-lm(LogFittedAR~LogPreyBM+LogPredBM+Temp_c, data=df_no)
summary(m1)

drop1(m1,test="F")

anova(m1)

step(m1)

```

B. Handling times
--
**Handling time ~ Predator Body mass+Prey Body Mass+Temp_c**

```{r echo=FALSE}

m2<-lm(LogFittedH_day~LogPreyBM+LogPredBM+Temp_c, data=df_no)
summary(m2)

drop1(m2,test="F")

anova(m2)

```

**Handling time ~ Prey/Predator body mass+Temp**

```{r echo=FALSE}

m3<-lm(log10(Fittted.h..day.)~log10(Prey.mass..mg./Predator.mass..mg.)+Temp..C.., data=forage_db)
summary(m3)

drop1(m3,test="F")

anova(m3)

anova(m2,m3)
```

Ecto- and Endotherm Grouping
---

It is possible that the relationships exist withing endo- and ectotherms' groups rather than with vert vs invert.This will also be handy becasue we would like to parameterise endo- and ectortherms differently in the Madingley. 

Unfortumately, FoRAGE databse does not distinguish between endo and ectotherms. We know that:

- Invertebrates (*n*=1520) are *ecothermic*

- Vertebrates (*n*= 470) can be either. Examples of ectothermic vertebrates are snales, reptiles, fish

- Angiosperms (*n* = 2) we can remove.

- Protozoans (*n*= 91) can also remove as likely not represented in the model. [Single-cell eukoryotes, ~0.01-0.05 mm in size thoygh up to 0.5 mm are faily common]

Let's have a look at the composition of our sample.

```{r }

mg1<-ggplot(forage_db, aes(Major.grouping.1))+geom_histogram(stat="count")


mg1+theme_bw(base_size = 13, base_family = "")+ theme(panel.border = element_blank(),panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),strip.background = element_rect(colour="white", fill="white"), strip.text.x = element_text(size = 14), legend.position = "bottom", legend.title=element_blank())+ theme(axis.text.x = element_text(angle = 90))+theme(axis.title.x=element_blank())


#Share of groups 1 subgroups in invertebrates

invertGr1<-ggplot(forage_db [forage_db$Vert.invert!="Angiosperm" & forage_db$Vert.invert!="Protozoan",], aes(Vert.invert))+geom_bar(aes(fill=Major.grouping.1))
invertGr1+theme_bw(base_size = 13, base_family = "")+ theme(panel.border = element_blank(),panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),strip.background = element_rect(colour="white", fill="white"), strip.text.x = element_text(size = 14), legend.position = "bottom", legend.title=element_blank())+theme(axis.title.x=element_blank())+scale_fill_manual(values=mycol)

#Share of group 1 in vertebrates

db_vertInvert<-forage_db[forage_db$Vert.invert!="Angiosperm" & forage_db$Vert.invert!="Protozoan",]
#which(db_vertInvert$Vert.invert=="Protozoan")
table( db_vertInvert$Major.grouping.1,db_vertInvert$Vert.invert)
```


- Archnids = ectotherm 

- Fish = ectotherm

- Reptile = ecotherm

- Bird = endotherm

- Mammal = endotherm

```{r echo=FALSE}

forage_db$EctoEndo<-ifelse(forage_db$Major.grouping.1=="Bird" | forage_db$Major.grouping.1=="Mammal", "Endo", "Ecto" )
#lets check

table(forage_db$Major.grouping.1, forage_db$EctoEndo)
```
